When, why, and how to avoid, prefer, or tolerate inbreeding

### 2018-03-05 presentation/inbreeding.Rmd
Fix date

---
title: "When, why, and how to avoid, prefer, or tolerate inbreeding"
subtitle: "https://bradduthie.shinyapps.io/inbreeding"
author: "Brad Duthie"
date: "6 March 2018"
output: 
  ioslides_presentation: 
    widescreen: yes
runtime: shiny
---

>>>>

---
title: "When, why, and how to avoid, prefer, or tolerate inbreeding"
subtitle: "https://bradduthie.shinyapps.io/inbreeding"
author: "Brad Duthie"
date: "3 April 2018"
output: 
  ioslides_presentation: 
    widescreen: yes
runtime: shiny
---
